---
title: "Mack Model Comparison"
output: html_notebook
---

Trying to reproduce the results of Glenn Myers Stochastic Loss Reserving Mack Model comparison

```{r}
suppressPackageStartupMessages({
    library(ChainLadder)
    library(dplyr)
})

inc_loss <- readRDS(glue::glue("{here::here()}/cache/ill_incloss.rds"))

# need to separate "real" data from values in checking
# ay + lag <= 1998 (ay run from 1988 to 1997 with 10 years of lags)

known_loss <- inc_loss %>%
    mutate(ay = as.numeric(ay)) %>%
    filter(ay + lag <= 1998)


known_loss_triangle <- as.triangle(known_loss,
                                   origin = "lag", 
                                   dev = "ay", 
                                   value = "vals")

known_loss_triangle
```


So let's run the mack model from chainladder package

My understanding of the Mack model is that we're using triangle to estimate 
distribution of expected losses developemnt.


```{r}
(mack_estimate <- MackChainLadder(known_loss_triangle))
```

I want to reproduce table 4 from the paper

```{r}

results_tbl <- tibble::tibble(
    lag = seq_along(mack_estimate$f),
    devfactor = rev(cumprod(rev(mack_estimate$f))),
    sd = rev(mack_estimate$Mack.S.E[, 10])
)

final_vals <- filter(inc_loss, lag == 10) %>%
    mutate(ay = as.numeric(ay)) %>%
    select(ay, vals)

 

table4 <- known_loss %>% 
    filter(ay + lag == 1998) %>%
    inner_join(results_tbl, by = "lag") %>%
    inner_join(final_vals, by = "ay") %>%
    mutate(mack_est = vals.x * devfactor, cv = sd / mack_est, ay = as.character(ay)) %>%
    select(ay, mack_est, sd, cv, actual = vals.y) %>%
    bind_rows(tibble(ay = "total", 
                     mack_est = sum(.$mack_est), 
                     sd = mack_estimate$Total.Mack.S.E,
                     cv = sd / mack_est,
                     actual = sum(.$actual))
              )

total_row <- table4[11, ]

dist_cv <- total_row$sd /total_row$mack_est
dist_mean <- total_row$mack_est
useful_val <- dist_cv^2 + 1

sd_log <- sqrt(log(useful_val))
mean_log <- log(dist_mean) - 0.5 * log(useful_val)


table4

```

And the percentile of the total row assuming lognormal as G.M. does is `r sprintf("%2.1f%%", plnorm(total_row$actual, meanlog = mean_log, sdlog = sd_log) * 100)`

